---
# Aridhia DRE Cohort Builder - Analysis Report
# Supports single-schema and multi-schema cohorts (v7).
# v7: Universal-outcome fallback + Cox section + reduced font sizes.
# Re-download from the app Export tab if you have an older version.
title: "`r params$cohort_name` - Cohort Analysis Report"
date: "`r format(Sys.Date(), '%d %B %Y')`"
author: "Generated by Aridhia DRE Cohort Builder"
output:
  word_document:
    toc: true
    toc_depth: 2
    number_sections: true
params:
  schema:
    label: "OMOP schema name(s) - comma-separated for multi-schema"
    value: ""
    input: text
  cohort_def_path:
    label: "Path to cohort definition JSON"
    value: ""
    input: text
  cohort_name:
    label: "Cohort name"
    value: "Cohort Analysis"
    input: text
  outcome_domain:
    label: "Outcome domain for survival analysis"
    value: "condition"
    input: select
    choices: [condition, drug, procedure, measurement, observation, death]
  outcome_concept_ids:
    label: "Outcome concept IDs (comma-separated, leave blank for all)"
    value: ""
    input: text
  cox_lookback_days:
    label: "Covariate lookback window (days)"
    value: 365
    input: numeric
  trt_followup_days:
    label: "Treatment pathway follow-up window (days)"
    value: 365
    input: numeric
  time_horizon_days:
    label: "Survival time horizon (days, 0 = no limit)"
    value: 0
    input: numeric
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE,
                      fig.width=7, fig.height=4.5, dpi=110)
required <- c("DBI","ggplot2","scales","survival","jsonlite","knitr")
for (pkg in required) {
  if (!requireNamespace(pkg, quietly=TRUE))
    stop(sprintf("Required package '%s' not installed.", pkg))
  suppressPackageStartupMessages(library(pkg, character.only=TRUE))
}
has_broom <- requireNamespace("broom", quietly=TRUE)
```

```{r connection, include=FALSE}
DRE_CONN <- tryCatch({ library(xaputils); xap.conn }, error=function(e) {
  message("xaputils not available."); NULL })
conn_valid <- function() !is.null(DRE_CONN)
if (!conn_valid())
  stop("No database connection. Knit inside an Aridhia DRE workspace.")
```

```{r helpers, include=FALSE}
`%||%` <- function(a,b) if (!is.null(a) && length(a)>0) a else b
as_pid  <- function(x) {
  if (inherits(x,"integer64")) return(as.numeric(as.character(x)))
  suppressWarnings(as.numeric(as.character(x)))
}
pid_sql <- function(x) {
  vals <- if (inherits(x,"integer64")) as.character(x)
          else sprintf("%.0f", suppressWarnings(as.numeric(as.character(x))))
  paste(vals, collapse=",")
}
pg_str <- function(s) paste0("'", gsub("'","''",as.character(s)), "'")
fq     <- function(schema,table) sprintf('"%s"."%s"', schema, table)
qq     <- function(x) sprintf('"%s"', x)
db_query <- function(sql) {
  if (!conn_valid()) stop("No connection.")
  withCallingHandlers(DBI::dbGetQuery(DRE_CONN, sql), warning=function(w) {
    if (grepl("unrecognized PostgreSQL|unknown data type",conditionMessage(w),ignore.case=TRUE))
      invokeRestart("muffleWarning") })
}
get_tables <- function(schema) {
  tryCatch({
    r <- db_query(sprintf("SELECT table_name FROM information_schema.tables
       WHERE table_schema=%s AND table_type='BASE TABLE' ORDER BY table_name", pg_str(schema)))
    tolower(r$table_name)
  }, error=function(e) character(0))
}
OMOP_TABLES <- c("observation_period","person","concept","concept_ancestor",
                 "condition_occurrence","drug_exposure","procedure_occurrence",
                 "measurement","observation","visit_occurrence","death")
get_col_map <- function(schema) {
  sql <- sprintf("SELECT lower(table_name) AS tbl, column_name AS col
     FROM information_schema.columns
     WHERE table_schema=%s AND lower(table_name) IN (%s)",
    pg_str(schema), paste(sapply(OMOP_TABLES,pg_str),collapse=","))
  r <- tryCatch(db_query(sql), error=function(e) NULL)
  if (is.null(r)||nrow(r)==0) return(list())
  names(r) <- tolower(names(r))
  result <- list()
  for (i in seq_len(nrow(r))) {
    tbl <- r$tbl[i]; col <- r$col[i]
    if (is.null(result[[tbl]])) result[[tbl]] <- list()
    result[[tbl]][[tolower(col)]] <- col
  }
  result
}
ac <- function(col_map,table,col) {
  actual <- col_map[[tolower(table)]][[tolower(col)]]
  qq(actual %||% col)
}
DOMAINS <- list(
  condition  =list(label="Diagnoses & Conditions",table="condition_occurrence",
                   concept_col="condition_concept_id",date_col="condition_start_date",person_col="person_id"),
  drug       =list(label="Medications",table="drug_exposure",
                   concept_col="drug_concept_id",date_col="drug_exposure_start_date",person_col="person_id"),
  procedure  =list(label="Procedures",table="procedure_occurrence",
                   concept_col="procedure_concept_id",date_col="procedure_date",person_col="person_id"),
  measurement=list(label="Measurements",table="measurement",
                   concept_col="measurement_concept_id",date_col="measurement_date",person_col="person_id"),
  observation=list(label="Observations",table="observation",
                   concept_col="observation_concept_id",date_col="observation_date",person_col="person_id"),
  death      =list(label="Death",table="death",
                   concept_col="cause_concept_id",date_col="death_date",person_col="person_id")
)
```

```{r params-parse, include=FALSE}
# Parse schema - comma-separated list for multi-schema support
SCHEMAS      <- trimws(strsplit(trimws(params$schema),",")[[1]])
SCHEMAS      <- SCHEMAS[nzchar(SCHEMAS)]
if (length(SCHEMAS)==0) stop("No schema specified.")
MULTI_SCHEMA <- length(SCHEMAS)>1
SCHEMA       <- SCHEMAS[1]
COHORT_NAME  <- trimws(params$cohort_name)
OUTCOME_DOM  <- trimws(params$outcome_domain)
COX_LOOKBACK <- as.integer(params$cox_lookback_days)
TRT_FOLLOWUP <- as.integer(params$trt_followup_days)
TIME_HORIZON <- as.integer(params$time_horizon_days)
if (is.na(TIME_HORIZON)||TIME_HORIZON<=0) TIME_HORIZON <- NA_integer_
OUTCOME_CIDS <- tryCatch({
  raw <- trimws(params$outcome_concept_ids)
  if (nzchar(raw)) as.integer(strsplit(raw,"[,\\s]+")[[1]]) else integer(0)
}, error=function(e) integer(0))
col_maps      <- setNames(lapply(SCHEMAS,get_col_map), SCHEMAS)
existing_tbls <- setNames(lapply(SCHEMAS,get_tables), SCHEMAS)
message("Schema(s): ", paste(SCHEMAS,collapse=", "))
```

```{r load-cohort, include=FALSE}
criteria <- list(); index_strategy <- "first_qualifying"
prior_obs_days <- NA_integer_; min_followup_days <- NA_integer_
def_path     <- trimws(params$cohort_def_path)
def_load_err <- NULL

# Fallback path resolution: if the supplied path is blank or missing,
# look in /home/workspace/files/Downloads for a recent *_definition_*.json
# matching the cohort name. This handles cases where the JSON path
# injection failed or the user moved files between exports.
if (!nzchar(def_path) || !file.exists(def_path)) {
  dl_dir <- "/home/workspace/files/Downloads"
  if (dir.exists(dl_dir)) {
    candidates <- list.files(dl_dir, pattern = "_definition_.+\\.json$",
                              full.names = TRUE)
    if (length(candidates) > 0) {
      # Prefer ones containing the cohort name; else the most recent
      nm_safe <- gsub("[^A-Za-z0-9_-]", "_", params$cohort_name %||% "")
      named <- if (nzchar(nm_safe))
        candidates[grepl(nm_safe, basename(candidates), fixed = TRUE)]
      else character(0)
      best <- if (length(named) > 0) named[order(file.mtime(named), decreasing = TRUE)][1]
              else candidates[order(file.mtime(candidates), decreasing = TRUE)][1]
      if (!is.na(best)) {
        message("[load-cohort] Falling back to: ", best)
        def_path <- best
      }
    }
  }
}

if (nzchar(def_path) && file.exists(def_path)) {
  raw <- tryCatch(jsonlite::fromJSON(def_path,simplifyVector=FALSE),
                  error=function(e) { def_load_err <<- conditionMessage(e); NULL })
  if (!is.null(raw)) {
    criteria <- lapply(raw$criteria %||% list(), function(c) {
      c$concept_ids  <- as.integer(c$concept_ids  %||% integer(0))
      c$gender_ids   <- as.integer(c$gender_ids   %||% integer(0))
      c$occur_min    <- as.integer(c$occur_min    %||% 1L)
      c$occur_max    <- if(is.null(c$occur_max))    NA_integer_ else as.integer(c$occur_max)
      c$window_start <- if(is.null(c$window_start)) NA_integer_ else as.integer(c$window_start)
      c$window_end   <- if(is.null(c$window_end))   NA_integer_ else as.integer(c$window_end)
      c$age_min      <- if(is.null(c$age_min))      NA_integer_ else as.integer(c$age_min)
      c$age_max      <- if(is.null(c$age_max))      NA_integer_ else as.integer(c$age_max)
      c$value_min    <- if(is.null(c$value_min))    NA_real_    else as.numeric(c$value_min)
      c$value_max    <- if(is.null(c$value_max))    NA_real_    else as.numeric(c$value_max)
      c$use_descendants <- isTRUE(c$use_descendants); c
    })
    COHORT_NAME       <- raw$cohort_name    %||% COHORT_NAME
    index_strategy    <- raw$index_strategy %||% "first_qualifying"
    prior_obs_days    <- if(is.null(raw$prior_obs_days))    NA_integer_ else as.integer(raw$prior_obs_days)
    min_followup_days <- if(is.null(raw$min_followup_days)) NA_integer_ else as.integer(raw$min_followup_days)
  }
}

# Validate: did we end up with criteria? If not, fail with a message that
# tells the truth about what's missing - the original generic "no results"
# error was misleading because it implied the SQL ran and returned zero
# rows, when in reality the SQL never ran at all.
if (length(criteria) == 0) {
  msg <- if (!nzchar(trimws(params$cohort_def_path))) {
    paste0("Cohort definition path is blank. The app's Export observer ",
           "likely failed to write the JSON definition file. ",
           "Re-export from the app; if the toast says 'Cohort definition not saved' ",
           "the JSON write failed and the Rmd cannot reconstruct the cohort.")
  } else if (!file.exists(trimws(params$cohort_def_path))) {
    sprintf(paste0("Cohort definition file not found at: %s\n",
                   "The file was either deleted, moved, or never written. ",
                   "Re-export from the app to generate a fresh pair (.Rmd + .json)."),
            trimws(params$cohort_def_path))
  } else if (!is.null(def_load_err)) {
    sprintf("Cohort definition file exists but could not be parsed as JSON: %s",
            def_load_err)
  } else {
    paste0("Cohort definition loaded but contains no criteria. ",
           "Make sure you built a cohort (at least one inclusion) before exporting.")
  }
  stop(msg)
}
build_cohort_sql <- function(schema,criteria,cohort_name="cohort",
                              index_strategy="first_qualifying",
                              prior_obs_days=NA_integer_,
                              min_followup_days=NA_integer_,col_map=list()) {
  ac2 <- function(tbl,col) ac(col_map,tbl,col)
  # Concept filter that honours use_descendants. Mirrors the app's logic in
  # build_cohort_sql so the report's SQL produces the same cohort as the
  # interactive app. Returns a string of the form "AND <cid_col> IN (...)"
  # or "AND <cid_col> IN (SELECT descendant_concept_id FROM concept_ancestor
  # WHERE ancestor_concept_id IN (...))" when descendants are requested.
  concept_filter_sql <- function(cid_col, concept_ids, use_descendants) {
    if (length(concept_ids) == 0) return("")
    ids_c <- paste(as.integer(concept_ids), collapse = ",")
    if (isTRUE(use_descendants)) {
      desc_col <- ac2("concept_ancestor", "descendant_concept_id")
      anc_col  <- ac2("concept_ancestor", "ancestor_concept_id")
      sprintf("\n       AND %s IN (SELECT %s FROM %s WHERE %s IN (%s))",
              cid_col, desc_col, fq(schema, "concept_ancestor"), anc_col, ids_c)
    } else {
      sprintf("\n       AND %s IN (%s)", cid_col, ids_c)
    }
  }
  inc <- Filter(function(c) c$type=="inclusion",criteria)
  exc <- Filter(function(c) c$type=="exclusion",criteria)
  if (length(inc)==0) return(NULL)
  idx_agg <- if(identical(index_strategy,"last_qualifying")) "MAX" else "MIN"
  idx_c <- inc[[1]]; idx_dom <- DOMAINS[[idx_c$domain]]
  conc_f <- concept_filter_sql(ac2(idx_dom$table, idx_dom$concept_col),
                                idx_c$concept_ids,
                                isTRUE(idx_c$use_descendants))
  lines <- c("WITH index_population AS (",
    sprintf("  SELECT %s AS person_id,",ac2(idx_dom$table,idx_dom$person_col)),
    sprintf("         %s(%s::date) AS index_date",idx_agg,ac2(idx_dom$table,idx_dom$date_col)),
    sprintf("  FROM   %s",fq(schema,idx_dom$table)),
    sprintf("  WHERE  1=1%s",conc_f),"  GROUP BY 1","  ),")
  inc_names <- c()
  for (i in seq_along(inc)[-1]) {
    cr <- inc[[i]]; dom <- DOMAINS[[cr$domain]]
    cf <- concept_filter_sql(ac2(dom$table, dom$concept_col),
                              cr$concept_ids,
                              isTRUE(cr$use_descendants))
    ws <- cr$window_start %||% NA_integer_; we <- cr$window_end %||% NA_integer_
    wj <- sprintf("\n  JOIN index_population ip ON t.%s=ip.person_id",ac2(dom$table,dom$person_col))
    ww <- if(!is.na(ws)&&!is.na(we))
      sprintf("\n       AND t.%s::date BETWEEN ip.index_date::date+INTERVAL '%d days' AND ip.index_date::date+INTERVAL '%d days'",
              ac2(dom$table,dom$date_col),ws,we)
    else if(!is.na(ws)) sprintf("\n       AND t.%s::date>=ip.index_date::date+INTERVAL '%d days'",ac2(dom$table,dom$date_col),ws)
    else if(!is.na(we)) sprintf("\n       AND t.%s::date<=ip.index_date::date+INTERVAL '%d days'",ac2(dom$table,dom$date_col),we)
    else ""
    cn <- sprintf("inc_%02d",i); inc_names <- c(inc_names,cn)
    lines <- c(lines,sprintf("  %s AS (",cn),
      sprintf("  SELECT t.%s AS person_id",ac2(dom$table,dom$person_col)),
      sprintf("  FROM   %s t%s",fq(schema,dom$table),wj),
      sprintf("  WHERE  1=1%s%s",cf,ww),"  GROUP BY 1","  ),")
  }
  prior_cl <- if(!is.na(prior_obs_days %||% NA_integer_)&&prior_obs_days>0L)
    sprintf("    AND op.%s::date<=ip.index_date::date-INTERVAL '%d days'",
            ac2("observation_period","observation_period_start_date"),prior_obs_days)
  else sprintf("    AND op.%s::date<=ip.index_date::date",
               ac2("observation_period","observation_period_start_date"))
  fup_cl <- if(!is.na(min_followup_days %||% NA_integer_)&&min_followup_days>0L)
    sprintf("    AND op.%s::date>=ip.index_date::date+INTERVAL '%d days'",
            ac2("observation_period","observation_period_end_date"),min_followup_days)
  else sprintf("    AND op.%s::date>=ip.index_date::date",
               ac2("observation_period","observation_period_end_date"))
  lines <- c(lines,"  obs_period AS (",
    sprintf("  SELECT DISTINCT op.%s AS person_id FROM %s op",
            ac2("observation_period","person_id"),fq(schema,"observation_period")),
    sprintf("  JOIN index_population ip ON op.%s=ip.person_id",
            ac2("observation_period","person_id")),
    prior_cl,fup_cl,"  ),")
  exc_names <- c()
  for (i in seq_along(exc)) {
    cr <- exc[[i]]; dom <- DOMAINS[[cr$domain]]
    cf2 <- concept_filter_sql(ac2(dom$table, dom$concept_col),
                               cr$concept_ids,
                               isTRUE(cr$use_descendants))
    cn  <- sprintf("exc_%02d",i); exc_names <- c(exc_names,cn)
    lines <- c(lines,sprintf("  %s AS (",cn),
      sprintf("  SELECT DISTINCT t.%s AS person_id FROM %s t",ac2(dom$table,dom$person_col),fq(schema,dom$table)),
      sprintf("  JOIN index_population ip ON t.%s=ip.person_id",ac2(dom$table,dom$person_col)),
      sprintf("  WHERE 1=1%s",cf2),"  ),")
  }
  join_incs <- if(length(inc_names)>0)
    paste(sapply(inc_names,function(n) sprintf("  JOIN %s ON %s.person_id=ip.person_id",n,n)),collapse="\n")
  else ""
  not_exc <- if(length(exc_names)>0)
    paste(sapply(exc_names,function(n) sprintf("  AND ip.person_id NOT IN (SELECT person_id FROM %s)",n)),collapse="\n")
  else ""
  lines <- c(lines,"  cohort AS (",
    "  SELECT ip.person_id, ip.index_date",
    "  FROM   index_population ip",
    "  JOIN   obs_period ON obs_period.person_id=ip.person_id",
    join_incs,sprintf("  WHERE 1=1\n%s",not_exc),"  )",
    "SELECT person_id, index_date,",
    "       ROW_NUMBER() OVER (ORDER BY person_id) AS cohort_rank",
    "FROM   cohort ORDER BY person_id")
  paste(lines,collapse="\n")
}
# Run per schema, tag, bind
cohort_result <- NULL; schema_errors <- character(0)
if (length(criteria)>0) {
  all_results <- list()
  for (sch in SCHEMAS) {
    cm  <- col_maps[[sch]]
    sql <- tryCatch(build_cohort_sql(sch,criteria,COHORT_NAME,index_strategy,
                                     prior_obs_days,min_followup_days,cm),
                    error=function(e) { message("SQL error [",sch,"]: ",e$message); NULL })
    if (!is.null(sql)) {
      r <- tryCatch({ res <- db_query(sql); names(res) <- tolower(names(res)); res },
                    error=function(e) {
                      schema_errors <<- c(schema_errors,sprintf("%s: %s",sch,conditionMessage(e))); NULL })
      if (!is.null(r)&&nrow(r)>0) { r$source_schema <- sch; all_results[[sch]] <- r }
    }
  }
  if (length(all_results)>0) {
    cohort_result <- do.call(rbind,all_results)
    cohort_result$cohort_rank <- seq_len(nrow(cohort_result))
  }
}
if (is.null(cohort_result)||nrow(cohort_result)==0) {
  msg <- paste0(
    "Cohort query executed but returned zero rows in every schema.\n",
    "Schemas tried: ", paste(SCHEMAS, collapse = ", "), "\n",
    "Criteria loaded: ", length(criteria), " (",
    sum(vapply(criteria, function(c) identical(c$type,"inclusion"), logical(1))),
    " inclusions, ",
    sum(vapply(criteria, function(c) identical(c$type,"exclusion"), logical(1))),
    " exclusions)\n",
    "Possible causes:\n",
    "  - Concept IDs do not exist in any selected schema\n",
    "  - Demographic / window filters exclude every patient\n",
    "  - Schema permissions prevent reading the required tables\n",
    if (length(schema_errors) > 0)
      paste0("\nSQL errors encountered:\n",
             paste("  -", schema_errors, collapse = "\n"))
    else ""
  )
  stop(msg)
}
N_COHORT     <- nrow(cohort_result)
MULTI_COHORT <- MULTI_SCHEMA && "source_schema" %in% names(cohort_result) &&
                length(unique(cohort_result$source_schema))>1
cohort_by_schema <- setNames(lapply(SCHEMAS, function(s)
  cohort_result[cohort_result$source_schema==s,,drop=FALSE]), SCHEMAS)
person_ids <- as_pid(cohort_result$person_id)
ids_sql    <- pid_sql(person_ids)
message("Total cohort: ", N_COHORT)
```

```{r theme, include=FALSE}
theme_report <- function() {
  ggplot2::theme_minimal(base_size=9) +
  ggplot2::theme(
    plot.background  = ggplot2::element_rect(fill="white",colour=NA),
    panel.background = ggplot2::element_rect(fill="white",colour=NA),
    panel.grid.major = ggplot2::element_line(colour="#E0E0E0",linewidth=0.3),
    panel.grid.minor = ggplot2::element_blank(),
    axis.text        = ggplot2::element_text(colour="#333333",size=7),
    axis.title       = ggplot2::element_text(colour="#333333",size=8),
    plot.title       = ggplot2::element_text(colour="#111111",size=9,face="bold"),
    plot.subtitle    = ggplot2::element_text(colour="#555555",size=7.5),
    plot.caption     = ggplot2::element_text(colour="#888888",size=7),
    legend.text      = ggplot2::element_text(colour="#333333",size=7),
    legend.title     = ggplot2::element_text(colour="#333333",size=7.5),
    legend.background= ggplot2::element_rect(fill="white",colour=NA),
    strip.text       = ggplot2::element_text(colour="#111111",size=8),
    axis.ticks       = ggplot2::element_blank()
  )
}
SCHEMA_COLS <- setNames(
  c("#1F4E79","#2E7D32","#7B1FA2","#BF360C","#00695C")[seq_along(SCHEMAS)],
  SCHEMAS)
rpt_table <- function(df,caption=NULL)
  knitr::kable(df,caption=caption,format="pandoc",row.names=FALSE)
```

```{r demographics, include=FALSE}
demo_list <- lapply(SCHEMAS, function(s) {
  cm <- col_maps[[s]]; et <- existing_tbls[[s]]
  if (!"person" %in% et) return(NULL)
  cs <- cohort_by_schema[[s]]; if(is.null(cs)||nrow(cs)==0) return(NULL)
  pids_s <- as_pid(cs$person_id); ids_s <- pid_sql(pids_s)
  pid_p <- ac(cm,"person","person_id"); yob_p <- ac(cm,"person","year_of_birth")
  gen_p <- ac(cm,"person","gender_concept_id")
  tmp_v <- paste(sprintf("(%.0f,'%s'::date)",pids_s,as.character(as.Date(cs$index_date))),collapse=",")
  r <- tryCatch({
    res <- db_query(sprintf(
      "WITH idx(person_id,index_date) AS (VALUES %s)
       SELECT p.%s AS person_id,
              EXTRACT(YEAR FROM i.index_date)::int-p.%s AS age_at_index,
              CASE WHEN p.%s=8532 THEN 1 ELSE 0 END AS is_female
       FROM %s p JOIN idx i ON i.person_id=p.%s WHERE p.%s IN (%s)",
      tmp_v,pid_p,yob_p,gen_p,fq(s,"person"),pid_p,pid_p,ids_s))
    names(res) <- tolower(names(res)); res$source_schema <- s; res
  }, error=function(e) NULL)
  r
})
demo_df <- if(any(!sapply(demo_list,is.null)))
  do.call(rbind,Filter(Negate(is.null),demo_list)) else NULL

# CCI
cci_map <- list(
  w1_mi=list(w=1,ids=c(4329847L,314666L,312327L)),
  w1_chf=list(w=1,ids=c(316139L,4229440L)),
  w1_pvd=list(w=1,ids=c(321596L,4108564L)),
  w1_cva=list(w=1,ids=c(372924L,375557L,443454L)),
  w1_dementia=list(w=1,ids=c(4182210L,378419L,373192L)),
  w1_copd=list(w=1,ids=c(255573L,4274024L)),
  w1_rheum=list(w=1,ids=c(80809L,257628L,134442L)),
  w1_pud=list(w=1,ids=c(4027663L,40481087L)),
  w1_mild_liver=list(w=1,ids=c(4064161L,4212540L)),
  w1_diabetes_unc=list(w=1,ids=c(201820L,442793L)),
  w2_diabetes_c=list(w=2,ids=c(201826L,4099651L)),
  w2_hemiplegia=list(w=2,ids=c(4291005L,432284L)),
  w2_renal=list(w=2,ids=c(46271022L,4030518L,443919L)),
  w2_cancer=list(w=2,ids=c(443392L,4248385L,4112853L,4029524L,4212540L)),
  w3_mod_liver=list(w=3,ids=c(4245975L,196454L,57345L)),
  w6_mets=list(w=6,ids=c(432851L,4212448L)),
  w6_aids=list(w=6,ids=c(439727L,4159981L))
)
cci_list <- lapply(SCHEMAS, function(s) {
  cm <- col_maps[[s]]; et <- existing_tbls[[s]]
  if (!"condition_occurrence" %in% et) return(NULL)
  cs <- cohort_by_schema[[s]]; if(is.null(cs)||nrow(cs)==0) return(NULL)
  pids_s <- as_pid(cs$person_id); ids_s <- pid_sql(pids_s)
  pid_col <- ac(cm,"condition_occurrence","person_id")
  cid_col <- ac(cm,"condition_occurrence","condition_concept_id")
  all_ids <- unique(unlist(lapply(cci_map,`[[`,"ids")))
  pts_df <- tryCatch(db_query(sprintf(
    "SELECT DISTINCT %s AS person_id,%s AS concept_id FROM %s
     WHERE %s IN (%s) AND %s IN (%s)",
    pid_col,cid_col,fq(s,"condition_occurrence"),
    pid_col,ids_s,cid_col,paste(all_ids,collapse=","))),error=function(e) NULL)
  df <- data.frame(person_id=pids_s,cci_score=0L,source_schema=s,stringsAsFactors=FALSE)
  if (!is.null(pts_df)&&nrow(pts_df)>0) {
    names(pts_df) <- tolower(names(pts_df))
    pts_df$person_id <- as_pid(pts_df$person_id)
    for (cat in cci_map) {
      hits <- unique(pts_df$person_id[pts_df$concept_id %in% cat$ids])
      if (length(hits)>0)
        df$cci_score[df$person_id %in% hits] <- df$cci_score[df$person_id %in% hits]+cat$w
    }
  }
  df
})
cci_df <- if(any(!sapply(cci_list,is.null))) do.call(rbind,Filter(Negate(is.null),cci_list)) else NULL

# Follow-up
followup_list <- lapply(SCHEMAS, function(s) {
  cm <- col_maps[[s]]; et <- existing_tbls[[s]]
  if (!"observation_period" %in% et) return(NULL)
  cs <- cohort_by_schema[[s]]; if(is.null(cs)||nrow(cs)==0) return(NULL)
  pids_s <- as_pid(cs$person_id); ids_s <- pid_sql(pids_s)
  op_pid <- ac(cm,"observation_period","person_id")
  op_end <- ac(cm,"observation_period","observation_period_end_date")
  tmp_v  <- paste(sprintf("(%.0f,'%s'::date)",pids_s,as.character(as.Date(cs$index_date))),collapse=",")
  tryCatch({
    r <- db_query(sprintf(
      "WITH idx(person_id,index_date) AS (VALUES %s)
       SELECT (MAX(op.%s::date)-i.index_date)::int AS days
       FROM %s op JOIN idx i ON i.person_id=op.%s
       WHERE op.%s IN (%s) AND op.%s::date>=i.index_date
       GROUP BY i.person_id,i.index_date",
      tmp_v,op_end,fq(s,"observation_period"),op_pid,op_pid,ids_s,op_end))
    names(r) <- tolower(names(r)); r$source_schema <- s; r
  }, error=function(e) NULL)
})
followup_df <- if(any(!sapply(followup_list,is.null)))
  do.call(rbind,Filter(Negate(is.null),followup_list)) else NULL
```

```{r survival-data, include=FALSE}
query_surv <- function(schema,col_map,cohort_sub,outcome_domain,outcome_concept_ids) {
  if(is.null(cohort_sub)||nrow(cohort_sub)==0) return(NULL)
  dom <- DOMAINS[[outcome_domain]]; if(is.null(dom)) return(NULL)
  et <- existing_tbls[[schema]]
  if(!tolower(dom$table) %in% et || !"observation_period" %in% et) return(NULL)
  pids <- as_pid(cohort_sub$person_id); ids_s <- pid_sql(pids)
  pid_col <- ac(col_map,dom$table,dom$person_col)
  dat_col <- ac(col_map,dom$table,dom$date_col)
  cid_col <- ac(col_map,dom$table,dom$concept_col)
  op_pid  <- ac(col_map,"observation_period","person_id")
  op_end  <- ac(col_map,"observation_period","observation_period_end_date")
  cf <- if(length(outcome_concept_ids)>0)
    sprintf("AND t.%s IN (%s)",cid_col,paste(as.integer(outcome_concept_ids),collapse=",")) else ""
  tmp_v <- paste(sprintf("(%.0f,'%s'::date)",pids,as.character(as.Date(cohort_sub$index_date))),collapse=",")
  sql <- sprintf(
    "WITH idx(person_id,index_date) AS (VALUES %s),
     outcomes AS (SELECT t.%s AS person_id,MIN(t.%s::date) AS event_date
       FROM %s t JOIN idx ON idx.person_id=t.%s
       WHERE t.%s IN (%s) AND t.%s::date>=idx.index_date %s GROUP BY 1),
     censoring AS (SELECT op.%s AS person_id,MAX(op.%s::date) AS censor_date
       FROM %s op JOIN idx ON idx.person_id=op.%s
       WHERE op.%s IN (%s) AND op.%s::date>=idx.index_date GROUP BY 1)
     SELECT i.person_id,COALESCE(o.event_date,c.censor_date,i.index_date) AS end_date,
            i.index_date,CASE WHEN o.person_id IS NOT NULL THEN 1 ELSE 0 END AS status
     FROM idx i LEFT JOIN outcomes o ON o.person_id=i.person_id
     LEFT JOIN censoring c ON c.person_id=i.person_id",
    tmp_v,pid_col,dat_col,fq(schema,dom$table),pid_col,
    pid_col,ids_s,dat_col,cf,
    op_pid,op_end,fq(schema,"observation_period"),op_pid,op_pid,ids_s,op_end)
  r <- tryCatch(db_query(sql),error=function(e) { message("[surv] ",e$message); NULL })
  if(is.null(r)||nrow(r)==0) return(NULL)
  names(r) <- tolower(names(r))
  r$time   <- pmax(as.numeric(as.Date(r$end_date)-as.Date(r$index_date)),0)
  r$status <- as.integer(r$status)
  r$source_schema <- schema
  r[,c("person_id","time","status","source_schema")]
}
surv_list <- lapply(SCHEMAS, function(s) query_surv(s,col_maps[[s]],cohort_by_schema[[s]],OUTCOME_DOM,OUTCOME_CIDS))
surv_data <- if(any(!sapply(surv_list,is.null))) do.call(rbind,Filter(Negate(is.null),surv_list)) else NULL
if(!is.null(surv_data)&&!is.na(TIME_HORIZON)&&TIME_HORIZON>0)
  surv_data$time <- pmin(surv_data$time,TIME_HORIZON)

# ── Survival section mode ───────────────────────────────────────────────────
# "configured" - the user supplied outcome concept IDs (or domain == death,
#                which is meaningful without a concept filter).
# "universal"  - no outcomes configured. Section 6 falls back to a panel of
#                three universally-applicable outcomes (mortality, first
#                inpatient visit, first ED visit) so the report stays useful.
# "none"       - even universal outcomes are unavailable in any schema
#                (e.g. death and visit_occurrence both missing).
KM_MODE <- if(length(OUTCOME_CIDS)>0 || identical(OUTCOME_DOM,"death")) "configured" else "universal"
```

```{r universal-outcomes-data, include=FALSE}
# Run three small per-cohort time-to-event analyses against universal
# outcomes that don't depend on the user picking concepts. Each is computed
# independently so a missing table in one schema doesn't kill the others.

# Visit concept IDs (OHDSI standard):
#   inpatient: 9201 (inpatient visit), 8717 (inpatient hospital), 262 (ER+IP)
#   ED:        9203 (emergency room visit)
INPATIENT_VISIT_IDS <- c(9201L, 8717L, 262L)
ED_VISIT_IDS        <- c(9203L)

# Mortality from death table - no concept filter needed
.universal_mortality <- function(s) {
  cm <- col_maps[[s]]; et <- existing_tbls[[s]]
  if (!"death" %in% et) return(NULL)
  cs <- cohort_by_schema[[s]]; if(is.null(cs)||nrow(cs)==0) return(NULL)
  pids_s <- as_pid(cs$person_id); ids_s <- pid_sql(pids_s)
  d_pid <- ac(cm,"death","person_id"); d_dat <- ac(cm,"death","death_date")
  op_pid <- ac(cm,"observation_period","person_id")
  op_end <- ac(cm,"observation_period","observation_period_end_date")
  tmp_v <- paste(sprintf("(%.0f,'%s'::date)",pids_s,as.character(as.Date(cs$index_date))),collapse=",")
  tryCatch({
    r <- db_query(sprintf(
      "WITH idx(person_id,index_date) AS (VALUES %s),
         deaths AS (SELECT t.%s AS person_id, t.%s::date AS event_date
           FROM %s t JOIN idx ON idx.person_id=t.%s
           WHERE t.%s IN (%s) AND t.%s::date>=idx.index_date),
         censoring AS (SELECT op.%s AS person_id, MAX(op.%s::date) AS censor_date
           FROM %s op JOIN idx ON idx.person_id=op.%s
           WHERE op.%s IN (%s) AND op.%s::date>=idx.index_date GROUP BY 1)
       SELECT i.person_id, i.index_date,
              COALESCE(d.event_date, c.censor_date, i.index_date) AS end_date,
              CASE WHEN d.person_id IS NOT NULL THEN 1 ELSE 0 END AS status
       FROM idx i
       LEFT JOIN deaths d   ON d.person_id=i.person_id
       LEFT JOIN censoring c ON c.person_id=i.person_id",
      tmp_v, d_pid, d_dat, fq(s,"death"), d_pid, d_pid, ids_s,
      op_pid, op_end, fq(s,"observation_period"), op_pid, op_pid, ids_s, op_end))
    names(r) <- tolower(names(r))
    r$time   <- pmax(as.numeric(as.Date(r$end_date)-as.Date(r$index_date)),0)
    r$status <- as.integer(r$status); r$source_schema <- s
    r[,c("person_id","time","status","source_schema")]
  }, error=function(e) { message("[univ.mortality] ",e$message); NULL })
}

# First visit after index, filtered by visit_concept_id
.universal_visit <- function(s, visit_ids, label) {
  cm <- col_maps[[s]]; et <- existing_tbls[[s]]
  if (!"visit_occurrence" %in% et) return(NULL)
  cs <- cohort_by_schema[[s]]; if(is.null(cs)||nrow(cs)==0) return(NULL)
  pids_s <- as_pid(cs$person_id); ids_s <- pid_sql(pids_s)
  v_pid <- ac(cm,"visit_occurrence","person_id")
  v_cid <- ac(cm,"visit_occurrence","visit_concept_id")
  v_dat <- ac(cm,"visit_occurrence","visit_start_date")
  op_pid <- ac(cm,"observation_period","person_id")
  op_end <- ac(cm,"observation_period","observation_period_end_date")
  tmp_v <- paste(sprintf("(%.0f,'%s'::date)",pids_s,as.character(as.Date(cs$index_date))),collapse=",")
  ids_filter <- paste(visit_ids, collapse=",")
  tryCatch({
    r <- db_query(sprintf(
      "WITH idx(person_id,index_date) AS (VALUES %s),
         visits AS (SELECT t.%s AS person_id, MIN(t.%s::date) AS event_date
           FROM %s t JOIN idx ON idx.person_id=t.%s
           WHERE t.%s IN (%s) AND t.%s IN (%s) AND t.%s::date>idx.index_date
           GROUP BY 1),
         censoring AS (SELECT op.%s AS person_id, MAX(op.%s::date) AS censor_date
           FROM %s op JOIN idx ON idx.person_id=op.%s
           WHERE op.%s IN (%s) AND op.%s::date>=idx.index_date GROUP BY 1)
       SELECT i.person_id, i.index_date,
              COALESCE(v.event_date, c.censor_date, i.index_date) AS end_date,
              CASE WHEN v.person_id IS NOT NULL THEN 1 ELSE 0 END AS status
       FROM idx i
       LEFT JOIN visits v   ON v.person_id=i.person_id
       LEFT JOIN censoring c ON c.person_id=i.person_id",
      tmp_v, v_pid, v_dat, fq(s,"visit_occurrence"), v_pid,
      v_pid, ids_s, v_cid, ids_filter, v_dat,
      op_pid, op_end, fq(s,"observation_period"), op_pid, op_pid, ids_s, op_end))
    names(r) <- tolower(names(r))
    r$time   <- pmax(as.numeric(as.Date(r$end_date)-as.Date(r$index_date)),0)
    r$status <- as.integer(r$status); r$source_schema <- s
    r[,c("person_id","time","status","source_schema")]
  }, error=function(e) { message("[univ.",label,"] ",e$message); NULL })
}

# First new condition recorded >=30 days post-index. Broad "did anything else
# happen" signal. Excludes the index event and same-day records to avoid
# trivially picking up the inclusion condition itself.
.universal_new_condition <- function(s) {
  cm <- col_maps[[s]]; et <- existing_tbls[[s]]
  if (!"condition_occurrence" %in% et) return(NULL)
  cs <- cohort_by_schema[[s]]; if(is.null(cs)||nrow(cs)==0) return(NULL)
  pids_s <- as_pid(cs$person_id); ids_s <- pid_sql(pids_s)
  c_pid <- ac(cm,"condition_occurrence","person_id")
  c_dat <- ac(cm,"condition_occurrence","condition_start_date")
  c_cid <- ac(cm,"condition_occurrence","condition_concept_id")
  op_pid <- ac(cm,"observation_period","person_id")
  op_end <- ac(cm,"observation_period","observation_period_end_date")
  tmp_v <- paste(sprintf("(%.0f,'%s'::date)",pids_s,as.character(as.Date(cs$index_date))),collapse=",")
  tryCatch({
    r <- db_query(sprintf(
      "WITH idx(person_id,index_date) AS (VALUES %s),
         events AS (SELECT t.%s AS person_id, MIN(t.%s::date) AS event_date
           FROM %s t JOIN idx ON idx.person_id=t.%s
           WHERE t.%s IN (%s) AND t.%s::date >= idx.index_date + INTERVAL '30 days'
             AND t.%s != 0
           GROUP BY 1),
         censoring AS (SELECT op.%s AS person_id, MAX(op.%s::date) AS censor_date
           FROM %s op JOIN idx ON idx.person_id=op.%s
           WHERE op.%s IN (%s) AND op.%s::date>=idx.index_date GROUP BY 1)
       SELECT i.person_id, i.index_date,
              COALESCE(e.event_date, c.censor_date, i.index_date) AS end_date,
              CASE WHEN e.person_id IS NOT NULL THEN 1 ELSE 0 END AS status
       FROM idx i
       LEFT JOIN events e   ON e.person_id=i.person_id
       LEFT JOIN censoring c ON c.person_id=i.person_id",
      tmp_v, c_pid, c_dat, fq(s,"condition_occurrence"), c_pid,
      c_pid, ids_s, c_dat, c_cid,
      op_pid, op_end, fq(s,"observation_period"), op_pid, op_pid, ids_s, op_end))
    names(r) <- tolower(names(r))
    r$time   <- pmax(as.numeric(as.Date(r$end_date)-as.Date(r$index_date)),0)
    r$status <- as.integer(r$status); r$source_schema <- s
    r[,c("person_id","time","status","source_schema")]
  }, error=function(e) { message("[univ.newcond] ",e$message); NULL })
}

# Build the universal datasets only when KM_MODE == "universal"
universal_datasets <- list()
if (identical(KM_MODE, "universal")) {
  mort_list <- lapply(SCHEMAS, .universal_mortality)
  ip_list   <- lapply(SCHEMAS, function(s) .universal_visit(s, INPATIENT_VISIT_IDS, "inpatient"))
  ed_list   <- lapply(SCHEMAS, function(s) .universal_visit(s, ED_VISIT_IDS, "ed"))
  nc_list   <- lapply(SCHEMAS, .universal_new_condition)

  bind_nonempty <- function(lst) {
    nn <- Filter(Negate(is.null), lst)
    if (length(nn)==0) NULL else do.call(rbind, nn)
  }
  mort_df <- bind_nonempty(mort_list)
  ip_df   <- bind_nonempty(ip_list)
  ed_df   <- bind_nonempty(ed_list)
  nc_df   <- bind_nonempty(nc_list)

  # Apply time horizon if set
  cap_h <- function(df) {
    if (is.null(df)) return(NULL)
    if (!is.na(TIME_HORIZON) && TIME_HORIZON>0) df$time <- pmin(df$time, TIME_HORIZON)
    df
  }
  universal_datasets <- list(
    mortality  = list(label="All-cause mortality",
                       sublabel="Time to death from any cause; censored at end of observation",
                       df = cap_h(mort_df)),
    inpatient  = list(label="First inpatient admission",
                       sublabel="Visit concepts: 9201, 8717, 262 (excludes index-day visits)",
                       df = cap_h(ip_df)),
    ed         = list(label="First emergency department visit",
                       sublabel="Visit concept: 9203 (excludes index-day visits)",
                       df = cap_h(ed_df)),
    new_cond   = list(label="First new condition recorded (>=30d post-index)",
                       sublabel="Any non-zero condition concept; 30-day buffer excludes index-related coding",
                       df = cap_h(nc_df))
  )
}
```

```{r top-conditions, include=FALSE}
top_cond_list <- lapply(SCHEMAS, function(s) {
  cm <- col_maps[[s]]; et <- existing_tbls[[s]]
  if(!all(c("condition_occurrence","concept") %in% et)) return(NULL)
  cs <- cohort_by_schema[[s]]; if(is.null(cs)||nrow(cs)==0) return(NULL)
  pids_s <- as_pid(cs$person_id); ids_s <- pid_sql(pids_s)
  pid_c  <- ac(cm,"condition_occurrence","person_id")
  cid_c  <- ac(cm,"condition_occurrence","condition_concept_id")
  cid_cn <- ac(cm,"concept","concept_id"); cnm_c <- ac(cm,"concept","concept_name")
  tryCatch({
    r <- db_query(sprintf(
      "SELECT c.%s AS concept_name,COUNT(DISTINCT co.%s)::int AS n
       FROM %s co JOIN %s c ON co.%s=c.%s
       WHERE co.%s IN (%s) AND co.%s!=0
       GROUP BY c.%s ORDER BY n DESC LIMIT 20",
      cnm_c,pid_c,fq(s,"condition_occurrence"),fq(s,"concept"),cid_c,cid_cn,
      pid_c,ids_s,cid_c,cnm_c))
    names(r) <- tolower(names(r)); r
  }, error=function(e) NULL)
})
top_cond_df <- if(any(!sapply(top_cond_list,is.null))) {
  all_c <- do.call(rbind,Filter(Negate(is.null),top_cond_list))
  if(nrow(all_c)>0) head(aggregate(n~concept_name,data=all_c,FUN=sum)[order(-aggregate(n~concept_name,data=all_c,FUN=sum)$n),],10L) else NULL
} else NULL

top_drug_list <- lapply(SCHEMAS, function(s) {
  cm <- col_maps[[s]]; et <- existing_tbls[[s]]
  if(!all(c("drug_exposure","concept") %in% et)) return(NULL)
  cs <- cohort_by_schema[[s]]; if(is.null(cs)||nrow(cs)==0) return(NULL)
  pids_s <- as_pid(cs$person_id); ids_s <- pid_sql(pids_s)
  pid_d  <- ac(cm,"drug_exposure","person_id")
  cid_d  <- ac(cm,"drug_exposure","drug_concept_id")
  cid_cn <- ac(cm,"concept","concept_id"); cnm_c <- ac(cm,"concept","concept_name")
  tryCatch({
    r <- db_query(sprintf(
      "SELECT c.%s AS concept_name,COUNT(DISTINCT de.%s)::int AS n
       FROM %s de JOIN %s c ON de.%s=c.%s
       WHERE de.%s IN (%s) AND de.%s!=0
       GROUP BY c.%s ORDER BY n DESC LIMIT 20",
      cnm_c,pid_d,fq(s,"drug_exposure"),fq(s,"concept"),cid_d,cid_cn,
      pid_d,ids_s,cid_d,cnm_c))
    names(r) <- tolower(names(r)); r
  }, error=function(e) NULL)
})
top_drug_df <- if(any(!sapply(top_drug_list,is.null))) {
  all_d <- do.call(rbind,Filter(Negate(is.null),top_drug_list))
  if(nrow(all_d)>0) head(aggregate(n~concept_name,data=all_d,FUN=sum)[order(-aggregate(n~concept_name,data=all_d,FUN=sum)$n),],10L) else NULL
} else NULL
```

```{r flags, include=FALSE}
surv_n_events <- if(!is.null(surv_data)) sum(surv_data$status==1L) else 0L
surv_n_total  <- if(!is.null(surv_data)) nrow(surv_data) else 0L
suppression_notice <- function(flag) paste0("> **Section not shown:** ",flag$reason)
warn_box <- function(msgs) {
  if(length(msgs)==0) return(invisible(NULL))
  cat(paste0("> **Note:** ",msgs,collapse="\n>\n> "),"\n\n")
}
# Whether universal panel has any usable data
universal_has_data <- identical(KM_MODE,"universal") &&
  any(vapply(universal_datasets, function(x) !is.null(x$df) && nrow(x$df)>0, logical(1)))
flags <- list(
  demo    =list(suppress=is.null(demo_df)||nrow(demo_df)==0,
                reason="The `person` table was not found or returned no rows."),
  survival=list(suppress=(identical(KM_MODE,"configured") && (is.null(surv_data)||surv_n_total==0)) ||
                          (identical(KM_MODE,"universal") && !universal_has_data),
                reason=if(identical(KM_MODE,"configured"))
                  sprintf("Survival data unavailable for `%s` domain.",DOMAINS[[OUTCOME_DOM]]$table)
                  else "No outcome concepts configured, and the universal-outcome fallback (mortality / inpatient / ED) found no usable data in any schema (death and visit_occurrence tables both absent or empty)."),
  cox     =list(suppress=surv_n_events<10,
                reason=sprintf("Cox requires >=10 events. Only %d observed.",surv_n_events)),
  concepts=list(suppress=!any(sapply(SCHEMAS,function(s)"concept" %in% existing_tbls[[s]])),
                reason="The `concept` table not found in any schema.")
)
```

# 1. Study Overview

```{r overview-table}
obs_row <- if(!is.null(followup_df)&&nrow(followup_df)>0)
  sprintf("%.1f (IQR: %.0f-%.0f yr)",
          median(followup_df$days,na.rm=TRUE)/365.25,
          quantile(followup_df$days,.25,na.rm=TRUE)/365.25,
          quantile(followup_df$days,.75,na.rm=TRUE)/365.25) else "-"
overview_df <- data.frame(
  Parameter=c("Cohort name","Schema(s)","Multi-schema","Analysis date",
               "Total cohort N","Follow-up median","Outcome domain","Events"),
  Value=c(COHORT_NAME,paste(SCHEMAS,collapse=" + "),if(MULTI_COHORT)"Yes" else "No",
          format(Sys.Date(),"%d %B %Y"),format(N_COHORT,big.mark=","),obs_row,
          DOMAINS[[OUTCOME_DOM]]$label %||% OUTCOME_DOM,
          if(!is.null(surv_data)) sprintf("%s (%.1f%%)",format(sum(surv_data$status),big.mark=","),
                                          100*mean(surv_data$status)) else "-"),
  stringsAsFactors=FALSE)
rpt_table(overview_df,"Study overview")
```

```{r schema-n-table}
if (MULTI_COHORT) {
  schema_n <- vapply(SCHEMAS, function(s) {
    cs <- cohort_by_schema[[s]]
    if (is.null(cs)) 0L else nrow(cs)
  }, integer(1))
  sn_df <- data.frame(Schema=SCHEMAS,
    N=schema_n,
    Pct=sprintf("%.1f%%", 100*schema_n/max(N_COHORT,1L)),
    stringsAsFactors=FALSE)
  rpt_table(sn_df,"Cohort size by schema")
}
```

```{r analysis-config-table}
# Surface what the report was generated with - empty outcome IDs is the
# most common cause of misleading survival plots; this makes it visible.
cids_display <- if (length(OUTCOME_CIDS)>0) paste(OUTCOME_CIDS, collapse=", ") else "(none configured)"
horizon_display <- if (is.na(TIME_HORIZON)||TIME_HORIZON<=0) "(no limit)" else sprintf("%d days", TIME_HORIZON)
mode_display <- switch(KM_MODE,
  configured = "Configured outcome (see below)",
  universal  = "Universal-outcome fallback (no concepts configured)",
  none       = "Not available"
)
cfg_df <- data.frame(
  Parameter=c("Outcome domain","Outcome concept IDs","Time horizon",
              "Survival section mode","Covariate lookback (Cox)"),
  Value=c(DOMAINS[[OUTCOME_DOM]]$label %||% OUTCOME_DOM,
          cids_display, horizon_display, mode_display,
          sprintf("%d days", COX_LOOKBACK)),
  stringsAsFactors=FALSE)
rpt_table(cfg_df, "Analysis configuration")
```

---

# 2. Cohort Definition

```{r criteria-table}
if (length(criteria)>0) {
  crit_rows <- lapply(criteria, function(c) {
    dom  <- DOMAINS[[c$domain]]
    type <- if(c$type=="inclusion") "Inclusion" else "Exclusion"
    concepts <- if(length(c$concept_ids)>0) paste(c$concept_ids,collapse=", ") else "(all)"
    ws <- c$window_start %||% NA; we <- c$window_end %||% NA
    win <- if(!is.na(ws)&&!is.na(we)) sprintf("%d to %d days",ws,we)
           else if(!is.na(ws)) sprintf(">=%d days",ws)
           else if(!is.na(we)) sprintf("<=%d days",we) else "Any time"
    data.frame(Type=type,Domain=dom$label %||% c$domain,Concepts=concepts,Window=win,stringsAsFactors=FALSE)
  })
  rpt_table(do.call(rbind,crit_rows),"Inclusion and exclusion criteria")
} else cat("*No criteria loaded.*\n")
```

---

# 3. Baseline Characteristics

```{r table1}
age_rows <- if(!is.null(demo_df)&&"age_at_index" %in% names(demo_df)) {
  ages <- demo_df$age_at_index[!is.na(demo_df$age_at_index)]
  list(c("Age (mean +/- SD)",sprintf("%.1f +/- %.1f",mean(ages),sd(ages))),
       c("Age (median [IQR])",sprintf("%.0f [%.0f-%.0f]",median(ages),quantile(ages,.25),quantile(ages,.75))),
       c("Age <18",sprintf("%d (%.1f%%)",sum(ages<18),100*mean(ages<18))),
       c("Age 18-39",sprintf("%d (%.1f%%)",sum(ages>=18&ages<40),100*mean(ages>=18&ages<40))),
       c("Age 40-59",sprintf("%d (%.1f%%)",sum(ages>=40&ages<60),100*mean(ages>=40&ages<60))),
       c("Age 60-79",sprintf("%d (%.1f%%)",sum(ages>=60&ages<80),100*mean(ages>=60&ages<80))),
       c("Age >=80",sprintf("%d (%.1f%%)",sum(ages>=80),100*mean(ages>=80))))
} else list(c("Age","N/A"))
sex_rows <- if(!is.null(demo_df)&&"is_female" %in% names(demo_df)) {
  fem <- demo_df$is_female
  list(c("Female",sprintf("%d (%.1f%%)",sum(fem==1,na.rm=TRUE),100*mean(fem==1,na.rm=TRUE))),
       c("Male",  sprintf("%d (%.1f%%)",sum(fem==0,na.rm=TRUE),100*mean(fem==0,na.rm=TRUE))))
} else list(c("Sex","N/A"))
cci_rows <- if(!is.null(cci_df)) {
  sc <- cci_df$cci_score
  list(c("CCI median [IQR]",sprintf("%.0f [%.0f-%.0f]",median(sc),quantile(sc,.25),quantile(sc,.75))),
       c("CCI=0",sprintf("%d (%.1f%%)",sum(sc==0),100*mean(sc==0))),
       c("CCI 1-2",sprintf("%d (%.1f%%)",sum(sc>=1&sc<=2),100*mean(sc>=1&sc<=2))),
       c("CCI>=3",sprintf("%d (%.1f%%)",sum(sc>=3),100*mean(sc>=3))))
} else list(c("CCI","N/A"))
fu_rows <- if(!is.null(followup_df)&&nrow(followup_df)>0) {
  dy <- followup_df$days
  list(c("Follow-up days median [IQR]",sprintf("%.0f [%.0f-%.0f]",
         median(dy,na.rm=TRUE),quantile(dy,.25,na.rm=TRUE),quantile(dy,.75,na.rm=TRUE))))
} else list(c("Follow-up","N/A"))
all_rows <- c(list(c(sprintf("N = %s",format(N_COHORT,big.mark=",")),"")),age_rows,sex_rows,cci_rows,fu_rows)
rpt_table(data.frame(Characteristic=sapply(all_rows,`[[`,1),
                     Value=sapply(all_rows,`[[`,2),stringsAsFactors=FALSE),
          "Table 1. Baseline characteristics")
```

---

# 4. Cohort Entry Over Time

```{r entry-plot, fig.height=3.5}
dates <- tryCatch(as.Date(cohort_result$index_date),error=function(e) NULL)
if (!is.null(dates)&&!all(is.na(dates))) {
  ts_df <- data.frame(
    period=sprintf("%s Q%d",format(dates,"%Y"),
                   as.integer(ceiling(as.integer(format(dates,"%m"))/3))),
    schema=if(MULTI_COHORT) cohort_result$source_schema else SCHEMA)
  tbl <- as.data.frame(table(ts_df$period,ts_df$schema))
  names(tbl) <- c("period","schema","n"); tbl$n <- as.integer(tbl$n)
  tbl <- tbl[order(tbl$period),]; tbl$period <- factor(tbl$period,levels=unique(tbl$period))
  p <- ggplot2::ggplot(tbl,ggplot2::aes(x=period,y=n,fill=schema)) +
    ggplot2::geom_col(position="stack",width=0.7) +
    ggplot2::labs(x=NULL,y="Patients",fill="Schema",title="Cohort Entry by Quarter") +
    theme_report() +
    ggplot2::theme(axis.text.x=ggplot2::element_text(angle=45,hjust=1,size=7))
  p <- p + ggplot2::scale_fill_manual(values=SCHEMA_COLS, guide=if(MULTI_COHORT) "legend" else "none")
  p
} else cat("*Index dates not available.*")
```

---

# 5. Top Diagnoses and Medications

```{r concepts-guard, results="asis"}
if(flags$concepts$suppress) cat(suppression_notice(flags$concepts),"\n")
```

```{r top-cond-plot, fig.height=3.8}
if(!is.null(top_cond_df)&&nrow(top_cond_df)>0) {
  df <- top_cond_df
  df$label <- ifelse(nchar(df$concept_name)>45,paste0(substr(df$concept_name,1,43),"..."),df$concept_name)
  df$pct <- 100*df$n/N_COHORT; df$label <- factor(df$label,levels=rev(df$label))
  ggplot2::ggplot(df,ggplot2::aes(x=pct,y=label)) +
    ggplot2::geom_col(fill="#1F4E79",width=0.7) +
    ggplot2::geom_text(ggplot2::aes(label=sprintf("%.1f%%",pct)),hjust=-0.1,size=2.8,colour="#333333") +
    ggplot2::scale_x_continuous(expand=ggplot2::expansion(mult=c(0,.2)),labels=function(x) paste0(x,"%")) +
    ggplot2::labs(x="% of cohort",y=NULL,title="Top 10 Diagnoses",
                  subtitle=if(MULTI_COHORT) paste("Combined:",paste(SCHEMAS,collapse=", ")) else NULL) +
    theme_report()+ggplot2::theme(axis.text.y=ggplot2::element_text(size=8))
} else cat("*Condition data not available.*")
```

```{r top-drug-plot, fig.height=3.8}
if(!is.null(top_drug_df)&&nrow(top_drug_df)>0) {
  df <- top_drug_df
  df$label <- ifelse(nchar(df$concept_name)>45,paste0(substr(df$concept_name,1,43),"..."),df$concept_name)
  df$pct <- 100*df$n/N_COHORT; df$label <- factor(df$label,levels=rev(df$label))
  ggplot2::ggplot(df,ggplot2::aes(x=pct,y=label)) +
    ggplot2::geom_col(fill="#2E7D32",width=0.7) +
    ggplot2::geom_text(ggplot2::aes(label=sprintf("%.1f%%",pct)),hjust=-0.1,size=2.8,colour="#333333") +
    ggplot2::scale_x_continuous(expand=ggplot2::expansion(mult=c(0,.2)),labels=function(x) paste0(x,"%")) +
    ggplot2::labs(x="% of cohort",y=NULL,title="Top 10 Medications",
                  subtitle=if(MULTI_COHORT) paste("Combined:",paste(SCHEMAS,collapse=", ")) else NULL) +
    theme_report()+ggplot2::theme(axis.text.y=ggplot2::element_text(size=8))
} else cat("*Drug exposure data not available.*")
```

---

# 6. Survival Analysis

```{r surv-mode-explainer, results="asis"}
# Explain to the reader which mode we're in. This matters because the
# interpretation differs sharply between configured and universal modes.
if (identical(KM_MODE, "configured")) {
  cat(sprintf("Survival analysis configured for outcome domain **%s**",
              DOMAINS[[OUTCOME_DOM]]$label %||% OUTCOME_DOM))
  if (length(OUTCOME_CIDS)>0) {
    cat(sprintf(" with concept IDs: %s.\n\n", paste(OUTCOME_CIDS, collapse=", ")))
  } else if (identical(OUTCOME_DOM,"death")) {
    cat(" (any death record).\n\n")
  } else {
    cat(".\n\n")
  }
} else if (identical(KM_MODE, "universal")) {
  cat("No outcome concepts were configured in the app at export time. The plots below show time-to-event for three universal outcomes meaningful across cohort types: all-cause mortality, first inpatient admission, and first emergency-department visit. To analyse a specific outcome, configure outcome concepts on the Survival tab in the app and re-export the report.\n\n")
}
if(flags$survival$suppress) cat(suppression_notice(flags$survival),"\n")
```

```{r km-plot-configured, fig.height=4, eval=identical(KM_MODE,"configured")}
if(!is.null(surv_data)&&nrow(surv_data)>0) {
  if(MULTI_COHORT) {
    schema_fits <- lapply(SCHEMAS, function(s) {
      sd_s <- surv_data[surv_data$source_schema==s,]
      if(nrow(sd_s)==0) return(NULL)
      fit <- tryCatch(survival::survfit(survival::Surv(time,status)~1,data=sd_s),error=function(e) NULL)
      if(is.null(fit)) return(NULL)
      df <- data.frame(time=c(0,fit$time),surv=c(1,fit$surv),
                       upper=c(1,fit$upper),lower=c(1,fit$lower),schema=s)
      df[!is.na(df$surv),]
    })
    km_all <- do.call(rbind,Filter(Negate(is.null),schema_fits))
    if(!is.null(km_all)&&nrow(km_all)>0)
      ggplot2::ggplot(km_all,ggplot2::aes(x=time,y=surv,colour=schema,fill=schema)) +
        ggplot2::geom_ribbon(ggplot2::aes(ymin=lower,ymax=upper),alpha=0.10,colour=NA) +
        ggplot2::geom_step(linewidth=1.0) +
        ggplot2::scale_colour_manual(values=SCHEMA_COLS) +
        ggplot2::scale_fill_manual(values=SCHEMA_COLS) +
        ggplot2::scale_y_continuous(labels=scales::percent_format(accuracy=1),limits=c(0,1),expand=c(.01,0)) +
        ggplot2::scale_x_continuous(labels=function(x) format(x,big.mark=","),expand=c(.01,0)) +
        ggplot2::labs(x="Days from index",y="Survival probability",colour="Schema",fill="Schema",
                      title=sprintf("Kaplan-Meier - %s",DOMAINS[[OUTCOME_DOM]]$label %||% OUTCOME_DOM),
                      subtitle=sprintf("N=%s | Events=%s (%.1f%%)",
                        format(nrow(surv_data),big.mark=","),format(sum(surv_data$status),big.mark=","),
                        100*mean(surv_data$status))) +
        theme_report()
  } else {
    fit <- tryCatch(survival::survfit(survival::Surv(time,status)~1,data=surv_data),error=function(e) NULL)
    if(!is.null(fit)) {
      km_df <- data.frame(time=c(0,fit$time),surv=c(1,fit$surv),upper=c(1,fit$upper),lower=c(1,fit$lower))
      km_df <- km_df[!is.na(km_df$surv),]
      med <- tryCatch(quantile(fit,.5)$quantile,error=function(e) NA_real_)
      p <- ggplot2::ggplot(km_df,ggplot2::aes(x=time,y=surv)) +
        ggplot2::geom_ribbon(ggplot2::aes(ymin=lower,ymax=upper),fill="#1F4E79",alpha=0.15,colour=NA) +
        ggplot2::geom_step(colour="#1F4E79",linewidth=1.1)
      if(!is.na(med)&&is.finite(med))
        p <- p+ggplot2::geom_vline(xintercept=med,linetype="dashed",colour="#C0392B",linewidth=0.7)
      p+ggplot2::scale_y_continuous(labels=scales::percent_format(accuracy=1),limits=c(0,1),expand=c(.01,0))+
        ggplot2::scale_x_continuous(labels=function(x) format(x,big.mark=","),expand=c(.01,0))+
        ggplot2::labs(x="Days from index",y="Survival probability",
                      title=sprintf("Kaplan-Meier - %s",DOMAINS[[OUTCOME_DOM]]$label %||% OUTCOME_DOM),
                      subtitle=sprintf("N=%s | Events=%s (%.1f%%)",
                        format(nrow(surv_data),big.mark=","),
                        format(sum(surv_data$status),big.mark=","),
                        100*mean(surv_data$status)))+
        theme_report()
    }
  }
} else cat("*Survival data not available.*")
```

```{r universal-km-helper, include=FALSE, eval=identical(KM_MODE,"universal")}
# Render one universal-outcome KM. Returns a ggplot or NULL if data missing.
.universal_km_plot <- function(spec) {
  df <- spec$df
  if (is.null(df) || nrow(df) == 0) return(NULL)
  fit <- tryCatch(survival::survfit(survival::Surv(time, status) ~ 1, data = df),
                   error = function(e) NULL)
  if (is.null(fit)) return(NULL)
  n_total  <- nrow(df)
  n_events <- sum(df$status == 1L)
  pct      <- 100 * n_events / max(n_total, 1L)
  med <- tryCatch(quantile(fit, .5)$quantile, error = function(e) NA_real_)
  med_label <- if (!is.na(med) && is.finite(med))
    sprintf("median %s d", format(round(med), big.mark = ",")) else "median not reached"
  km_df <- data.frame(time = c(0, fit$time), surv = c(1, fit$surv),
                       upper = c(1, fit$upper), lower = c(1, fit$lower))
  km_df <- km_df[!is.na(km_df$surv), ]
  p <- ggplot2::ggplot(km_df, ggplot2::aes(x = time, y = surv)) +
    ggplot2::geom_ribbon(ggplot2::aes(ymin = lower, ymax = upper),
                          fill = "#1F4E79", alpha = 0.15, colour = NA) +
    ggplot2::geom_step(colour = "#1F4E79", linewidth = 1.0)
  if (!is.na(med) && is.finite(med))
    p <- p + ggplot2::geom_vline(xintercept = med, linetype = "dashed",
                                  colour = "#C0392B", linewidth = 0.6)
  p +
    ggplot2::scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                                 limits = c(0, 1), expand = c(.01, 0)) +
    ggplot2::scale_x_continuous(labels = function(x) format(x, big.mark = ","),
                                 expand = c(.01, 0)) +
    ggplot2::labs(x = "Days from index", y = "Survival",
                  title = spec$label,
                  subtitle = sprintf("N=%s | Events=%s (%.1f%%) | %s",
                                      format(n_total, big.mark = ","),
                                      format(n_events, big.mark = ","),
                                      pct, med_label),
                  caption = spec$sublabel) +
    theme_report() +
    ggplot2::theme(plot.title = ggplot2::element_text(size = 8),
                   plot.subtitle = ggplot2::element_text(size = 7),
                   plot.caption = ggplot2::element_text(size = 6.5,
                                                         colour = "#888888"))
}
```

```{r universal-km-mortality, fig.height=3.2, eval=identical(KM_MODE,"universal")}
spec <- universal_datasets$mortality
p <- .universal_km_plot(spec)
if (!is.null(p)) p else cat("*All-cause mortality: ",
  if (is.null(spec$df)) "death table not found or empty in any schema." else "no usable data.",
  "*\n\n", sep="")
```

```{r universal-km-inpatient, fig.height=3.2, eval=identical(KM_MODE,"universal")}
spec <- universal_datasets$inpatient
p <- .universal_km_plot(spec)
if (!is.null(p)) p else cat("*First inpatient admission: ",
  if (is.null(spec$df)) "visit_occurrence table not found or empty in any schema." else "no usable data.",
  "*\n\n", sep="")
```

```{r universal-km-ed, fig.height=3.2, eval=identical(KM_MODE,"universal")}
spec <- universal_datasets$ed
p <- .universal_km_plot(spec)
if (!is.null(p)) p else cat("*First ED visit: ",
  if (is.null(spec$df)) "visit_occurrence table not found or empty in any schema." else "no usable data.",
  "*\n\n", sep="")
```

```{r universal-km-newcond, fig.height=3.2, eval=identical(KM_MODE,"universal")}
spec <- universal_datasets$new_cond
p <- .universal_km_plot(spec)
if (!is.null(p)) p else cat("*First new condition: ",
  if (is.null(spec$df)) "condition_occurrence table not found or empty in any schema." else "no usable data.",
  "*\n\n", sep="")
```

---

# 7. Adjusted Survival (Cox model)

```{r cox-mode-explainer, results="asis"}
# Section header explains mode. Mirrors the KM mode section above.
if (identical(KM_MODE, "configured")) {
  cat("Cox model fit on the configured outcome, with age, sex, and CCI score as adjustment covariates.\n\n")
} else if (identical(KM_MODE, "universal")) {
  cat("No outcome configured in the app at export time. The Cox models below fit two universal outcomes (all-cause mortality and first inpatient admission) on the cohort, adjusted for age, sex, and CCI score. These provide a baseline adjusted-hazard view; for a full domain-specific Cox with extracted condition/drug covariates, run the Cox tab in the app and re-export.\n\n")
}
```

```{r cox-helpers, include=FALSE}
# Lightweight Cox: fit survival ~ age + sex + cci, return a tidy coefficient
# data frame and a small forest plot. Returns NULL when EPV is insufficient
# or any prerequisite is missing.

# Per-cohort baseline covariate matrix (one row per person).
# Cached because both configured-mode and universal-mode Cox use it.
.cox_baseline_cov <- local({
  cached <- NULL
  function() {
    if (!is.null(cached)) return(cached)
    if (is.null(demo_df) || nrow(demo_df) == 0) return(NULL)
    cov <- demo_df[, c("person_id", "age_at_index", "is_female", "source_schema")]
    if (!is.null(cci_df)) {
      cov <- merge(cov, cci_df[, c("person_id", "cci_score", "source_schema")],
                   by = c("person_id", "source_schema"), all.x = TRUE)
      cov$cci_score[is.na(cov$cci_score)] <- 0L
    } else {
      cov$cci_score <- 0L
    }
    cached <<- cov
    cov
  }
})

.fit_cox_simple <- function(surv_df, outcome_label) {
  if (is.null(surv_df) || nrow(surv_df) == 0) return(NULL)
  n_events <- sum(surv_df$status == 1L)
  if (n_events < 10) {
    return(list(state = "epv", n_events = n_events, outcome_label = outcome_label))
  }
  cov <- .cox_baseline_cov()
  if (is.null(cov)) return(list(state = "no_covariates", outcome_label = outcome_label))
  # Merge by (person_id, source_schema) when multi, else person_id alone
  merge_by <- if ("source_schema" %in% names(surv_df) &&
                  "source_schema" %in% names(cov))
    c("person_id", "source_schema") else "person_id"
  cov2 <- cov[, c(merge_by, "age_at_index", "is_female", "cci_score")]
  surv_df$person_id <- as_pid(surv_df$person_id)
  cov2$person_id    <- as_pid(cov2$person_id)
  mdat <- merge(surv_df, cov2, by = merge_by, all.x = FALSE)
  mdat <- mdat[stats::complete.cases(mdat[, c("time", "status",
                                               "age_at_index", "is_female",
                                               "cci_score")]), ]
  if (nrow(mdat) == 0 || sum(mdat$status == 1L) < 10) {
    return(list(state = "epv", n_events = sum(mdat$status == 1L),
                outcome_label = outcome_label))
  }
  fit <- tryCatch(
    survival::coxph(survival::Surv(time, status) ~
                      age_at_index + is_female + cci_score, data = mdat),
    error = function(e) NULL)
  if (is.null(fit)) return(list(state = "fit_failed", outcome_label = outcome_label))
  s <- summary(fit)
  coef_df <- data.frame(
    covariate = rownames(s$coefficients),
    hr        = s$coefficients[, "exp(coef)"],
    ci_lo     = s$conf.int[, "lower .95"],
    ci_hi     = s$conf.int[, "upper .95"],
    p_value   = s$coefficients[, "Pr(>|z|)"],
    stringsAsFactors = FALSE
  )
  coef_df$label <- c(age_at_index = "Age (per year)",
                      is_female    = "Female (vs male)",
                      cci_score    = "CCI (per point)")[coef_df$covariate]
  coef_df$label[is.na(coef_df$label)] <- coef_df$covariate[is.na(coef_df$label)]
  coef_df$sig <- coef_df$p_value < 0.05
  list(state = "ok", outcome_label = outcome_label,
       n_persons = nrow(mdat), n_events = sum(mdat$status == 1L),
       coef_df = coef_df)
}

.cox_forest_plot <- function(res) {
  if (is.null(res) || !identical(res$state, "ok")) return(NULL)
  d <- res$coef_df
  d$label <- factor(d$label, levels = rev(d$label))
  d$ci_lo_plt <- pmax(d$ci_lo, 0.1)
  d$ci_hi_plt <- pmin(d$ci_hi, 10)
  ggplot2::ggplot(d, ggplot2::aes(x = hr, y = label, colour = sig)) +
    ggplot2::geom_vline(xintercept = 1, colour = "#C0392B",
                         linetype = "dashed", linewidth = 0.4) +
    ggplot2::geom_errorbarh(ggplot2::aes(xmin = ci_lo_plt, xmax = ci_hi_plt),
                              height = 0.25, linewidth = 0.6) +
    ggplot2::geom_point(size = 2.4) +
    ggplot2::scale_colour_manual(values = c("TRUE" = "#1F4E79", "FALSE" = "#999999"),
                                  labels = c("TRUE" = "p<0.05",
                                              "FALSE" = "p>=0.05"),
                                  name = NULL) +
    ggplot2::scale_x_log10(labels = function(x) sprintf("%.2f", x)) +
    ggplot2::labs(x = "Hazard Ratio (log scale, 95% CI)", y = NULL,
                  title = sprintf("Cox: %s", res$outcome_label),
                  subtitle = sprintf("N=%s persons, %s events",
                                      format(res$n_persons, big.mark = ","),
                                      format(res$n_events, big.mark = ","))) +
    theme_report() +
    ggplot2::theme(legend.position = "right",
                   legend.text = ggplot2::element_text(size = 6.5),
                   axis.text.y = ggplot2::element_text(size = 7))
}
```

```{r cox-configured, fig.height=2.8, eval=identical(KM_MODE,"configured")}
res <- .fit_cox_simple(surv_data,
                       sprintf("%s", DOMAINS[[OUTCOME_DOM]]$label %||% OUTCOME_DOM))
if (is.null(res)) {
  cat("*Cox not run: no survival data.*\n")
} else if (identical(res$state, "epv")) {
  cat(sprintf("*Cox not fit: only %d events observed (need >=10).*\n", res$n_events))
} else if (identical(res$state, "ok")) {
  p <- .cox_forest_plot(res)
  print(p)
  # Coefficient table beneath
  ct <- res$coef_df
  ct_df <- data.frame(
    Covariate = ct$label,
    HR        = sprintf("%.2f", ct$hr),
    `95% CI`  = sprintf("%.2f - %.2f", ct$ci_lo, ct$ci_hi),
    `p-value` = ifelse(ct$p_value < 0.001, "<0.001", sprintf("%.3f", ct$p_value)),
    stringsAsFactors = FALSE, check.names = FALSE)
  rpt_table(ct_df, sprintf("Cox coefficients - %s", res$outcome_label))
} else {
  cat(sprintf("*Cox not fit: state=%s.*\n", res$state))
}
```

```{r cox-universal-mortality, fig.height=2.8, eval=identical(KM_MODE,"universal")}
spec <- universal_datasets$mortality
res <- .fit_cox_simple(spec$df, "All-cause mortality")
if (is.null(res)) {
  cat("*Cox (mortality) not run: no mortality data.*\n")
} else if (identical(res$state, "epv")) {
  cat(sprintf("*Cox (mortality) not fit: only %d events observed (need >=10).*\n", res$n_events))
} else if (identical(res$state, "ok")) {
  print(.cox_forest_plot(res))
  ct <- res$coef_df
  ct_df <- data.frame(
    Covariate = ct$label,
    HR        = sprintf("%.2f", ct$hr),
    `95% CI`  = sprintf("%.2f - %.2f", ct$ci_lo, ct$ci_hi),
    `p-value` = ifelse(ct$p_value < 0.001, "<0.001", sprintf("%.3f", ct$p_value)),
    stringsAsFactors = FALSE, check.names = FALSE)
  rpt_table(ct_df, "Cox coefficients - All-cause mortality")
}
```

```{r cox-universal-inpatient, fig.height=2.8, eval=identical(KM_MODE,"universal")}
spec <- universal_datasets$inpatient
res <- .fit_cox_simple(spec$df, "First inpatient admission")
if (is.null(res)) {
  cat("*Cox (inpatient) not run: no inpatient data.*\n")
} else if (identical(res$state, "epv")) {
  cat(sprintf("*Cox (inpatient) not fit: only %d events observed (need >=10).*\n", res$n_events))
} else if (identical(res$state, "ok")) {
  print(.cox_forest_plot(res))
  ct <- res$coef_df
  ct_df <- data.frame(
    Covariate = ct$label,
    HR        = sprintf("%.2f", ct$hr),
    `95% CI`  = sprintf("%.2f - %.2f", ct$ci_lo, ct$ci_hi),
    `p-value` = ifelse(ct$p_value < 0.001, "<0.001", sprintf("%.3f", ct$p_value)),
    stringsAsFactors = FALSE, check.names = FALSE)
  rpt_table(ct_df, "Cox coefficients - First inpatient admission")
}
```

---

# 8. Methods

This report was generated using the **Aridhia DRE Cohort Builder**.

**Data source(s):** OMOP CDM v5.3/5.4, schema`r if(length(SCHEMAS)>1)"s" else ""`: `r paste(SCHEMAS,collapse=", ")`.

`r if(MULTI_COHORT) paste0("**Multi-schema cohort:** Criteria applied independently per schema and results combined. Per-schema N: ",paste(sapply(SCHEMAS,function(s) { cs <- cohort_by_schema[[s]]; paste0(s," (",if(is.null(cs)) 0L else nrow(cs),")") }),collapse=", "),".") else ""`

**Software:** R `r paste(R.version$major,R.version$minor,sep=".")`. Connection via xaputils::xap.conn.

---

# 9. Audit

```{r audit-table}
rpt_table(data.frame(
  Item=c("Generated","Schema(s)","Multi-schema","Cohort","N","Definition","R version"),
  Value=c(format(Sys.time(),"%Y-%m-%d %H:%M:%S"),paste(SCHEMAS,collapse=", "),
          if(MULTI_COHORT)"Yes" else "No",COHORT_NAME,format(N_COHORT,big.mark=","),
          if(nzchar(def_path)) def_path else "(none)",
          paste(R.version$major,R.version$minor,sep=".")),
  stringsAsFactors=FALSE),"Audit log")
```
